Trajipaq_sentiment_an

### 2023-08-16 1. Trajipaq_sentiment/2. Codes/Trajipaq_sentiment_an.Rmd
update

reg_WGI_can_2021 <- glm(formula = sentimapp_can_dico ~ wgi_origin_2021_score , data = trajipaq, family = "binomial") ## VD2 dichotomique
reg_WGI_can_2021_ctrl <- glm(formula = sentimapp_can_dico ~ wgi_origin_2021_score  + age + education + sexe + origine + revenu + langue_mat + religion + statut_mat , data = trajipaq, family = "binomial")#VD2 contrôlée par CSD

@@

```{r}
 stargazer(
  reg_WGI_can_arrival,
  reg_WGI_can_arrival_ctrl,
  reg_WGI_arrival_diff,
  reg_WGI_arrival_diff_ctrl,
  reg_WGI_can_2021,
  reg_WGI_can_2021_ctrl,
  reg_WGI_2021_diff,
  reg_WGI_2021_diff,
  reg_WGI_2021_diff_ctrl,
  title = "Results", 
  align = TRUE, 
  type = "text"
)

>>>>

reg_WGI_can_2021 <- glm(formula = sentimapp_can_dico ~ wgi_origin_2021_score, data = trajipaq, family = "binomial") ## VD2 dichotomique
reg_WGI_can_2021_ctrl <- glm(formula = sentimapp_can_dico ~ wgi_origin_2021_score  + age + education + sexe + origine + revenu + langue_mat + religion + statut_mat , data = trajipaq, family = "binomial")#VD2 contrôlée par CSD

@@

```{r}
 stargazer(
  reg_WGI_can_arrival,
  reg_WGI_can_arrival_ctrl,
  reg_WGI_arrival_diff,
  reg_WGI_arrival_diff_ctrl,
  reg_WGI_can_2021,
  reg_WGI_can_2021_ctrl,
  reg_WGI_2021_diff,
  reg_WGI_2021_diff_ctrl,
  title = "Results", 
  align = TRUE, 
  type = "text"
)
